Computer Science House Constitution

### 2025-12-02 constitution.tex

The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic year.
Any of these requirements may be waived by the Evals Director or an E-Board Vote.
\begin{enumerate}
	\item Attend at least six House Meetings
	\item Attend at least six directorship meetings
	\item Attend at least two Technical Seminars
\end{enumerate}

@@

\asubsection{Eligible Votes}
The number of Active Members who are eligible to vote on the issue.
Following the first Intro Eval of the academic semester, Active Members are only eligible to vote if they have completed the qualifications listed in \ref{Expectations of Voting Members}.
Officers of CSH retain voting eligibility on all matters directly pertaining to the duties of their held office regardless of \ref{Expectations of Voting Members}.

>>>>

The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic semester.
Any of these requirements may be waived by the Evals Director or an E-Board Vote.
\begin{enumerate}
	\item Attend at least six House Meetings
	\item Attend at least six directorship meetings
	\item Attend at least two Technical Seminars
\end{enumerate}

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.
The eligible voters for a vote are determined and fixed when the Voting Period begins.
Following the first Intro Eval of the academic semester, Active Members are only eligible to vote if they have completed the qualifications listed in \ref{Expectations of Voting Members}.
Officers of CSH retain voting eligibility on all matters directly pertaining to the duties of their held office regardless of \ref{Expectations of Voting Members}.
